---
title: "Chapter 3 Exercises"
output:
  pdf_document: default
  html_notebook: default
---


#Exercise 1

Lets load in the data file and take a look:
```{r}
dat=read.table("./ARM_Data/pyth/exercise2.1.dat",header=TRUE)
head(dat)
```
According to the text some of the data does not have y values; confirm that and create a subset of just the labelled data:
```{r}
#how many rows have y label
print(paste("Labeled: ", sum(!is.na(dat$y))))
#how many rows do not have y label
print(paste("Unlabeled: ",sum(is.na(dat$y))))
label<-dat[!is.na(dat$y),]
```

Lets take a look at the distribution of the predictors for the labelled data:
```{r}
plot(label[c('x1','x2')])
```

Now lets plot the response against each predictor, starting with x1:
```{r}
plot(label[c('x1','y')])
```
Not much of a relation on the margin...

Now x2:
```{r}
plot(label[c('x2','y')])
```
Oh that looks quite a bit stronger.

Now lets fit a linear model to the labelled data:
```{r}
fit = lm(label$y ~ label$x1 + label$x2)
summary(fit)
```


